Updates on the Exoplanet Orbit Database

### 2013-12-29 draft/ms.tex
Refine table: double check units and make descriptions brief.

% definition of symbols
\def\beq{\begin{equation}}
\def\eeq{\end{equation}}
\def\ergcms{erg~cm$^{-2}$~s$^{-1}$}
\def\ergs{erg~s$^{-1}$}
\def\mps{m~s$^{-1}$}
\def\msun{M_{\odot}}
\def\lsun{L_{\odot}}
\def\etal{~et~al.~}
\def\degree{^{\circ}}
\def\leq{\leqslant}
\def\geq{\geqslant}
\def\micron{$\mu$m}
\def\percm2{{\rm cm^{-2}}}
\def\peryr{yr$^{-1}$}
\def\kepler{\textit{Kepler}}
\def\spitzer{\textit{Spitzer}}
\def\micron{$\mu$m}

@@

Table: complete list of table parameters. Highlight the ones not
included in \cite{Wright2011}.

Figure: Figure of single planet page, to show updated transit
parameters and RV curves etc.?

@@

\rotate

@@

  \colhead{Field} & \colhead{Data Type} & \colhead{Meaning} &
  \colhead{Related Fields\tablenotemark{a}}

@@

OTHERNAME\tablenotemark{b}\dotfill & String & Other commonly used name of planet & \nodata \\

@@

RA, RA\_STRING\dotfill & Double, String & J2000 right ascension in decimal hours and in
sexagesimal string & \nodata  \\
DEC, DEC\_STRING\dotfill & Double, String & J2000 declination in decimal degrees and in
sexagesimal string & \nodata \\

@@

KDE\dotfill & Boolean & If true, then this planet appears in the
\kepler\ archive & \nodata \\
EOD\dotfill & Boolean & If true, then this planet has been vetted by the
exoplanets.org team & \nodata \\
MICROLENSING\dotfill & Boolean & If true, then this planet was detected via microlensing & \nodata \\ 
IMAGING\dotfill & Boolean & If true, then this planet was detected via imaging
& \nodata \\
TIMING\dotfill & Boolean & If true, then this planet was detected via timing & \nodata \\
ASTROMETRY\dotfill & Boolean & If true, then this planet was detected via
astrometric motion & \nodata \\

@@

DIST\dotfill & & Distance to planetary system based on parallax in parsecs & -UPPER, etc. \\

@@

T0\dotfill & Double & Epoch of periastron in HJD\tablenotemark{c}$-2,440,000$ & -UPPER, etc. \\

@@

systems only ZZZ still true?) & -UPPER, etc. \\

@@

function) in $M_{\rm Jup}$ & -UPPER, etc. \\

@@

MASS\dotfill & & & -UPPER, etc. \\
SEP\dotfill & & & -UPPER, etc. \\

@@

DEPTH\dotfill & Float & $(R_p/R_*)^2$ & -UPPER, etc. \\

@@

HJD\tablenotemark{c}$-2,440,000$ & -UPPER, etc. \\
R\dotfill & Float & Radius of the planet in Jupiter radii & -UPPER, etc. \\
AR\dotfill & $(a/R_*)$ & & -UPPER, etc. \\

@@

GRAVITY\dotfill & Float & $\log{g}$ (surface gravity) of the planet
calculated from transit parameters in cgs unit &

@@

SE\dotfill & Boolean & If true, at least one secondary eclipse has been detected in the wavelengths listed below & -REF,-URL \\
SEDEPTHJ\dotfill & & The secondary eclipse depth measured in the near
infrared J band centered at 1.25 \micron &
SEDEPTHH\dotfill & & The secondary eclipse depth measured in the near
infrared H band centered at 1.65 \micron & 
SEDEPTHKS\dotfill & & The secondary eclipse depth measured in the near
infrared Ks band centered at 2.15 \micron &
SEDEPTHKP\dotfill & & The secondary eclipse depth measured in the
Kepler photometry band in the optical from 400 to 865 nm &
SEDEPTH36\dotfill & & The secondary eclipse depth measured by
\spitzer\ in its IRAC1 band centered at 3.6 \micron &
SEDEPTH45\dotfill & & The secondary eclipse depth measured by \spitzer\
in its IRAC2 band centered at 4.5 \micron &
SEDEPTH58\dotfill & & The secondary eclipse depth measured by \spitzer\
in its IRAC2 band centered at 5.8 \micron & 
SEDEPTH80\dotfill & & The secondary eclipse depth measured by \spitzer\
in its IRAC2 band centered at 8.0 \micron &

@@

HJD\tablenotemark{c}$-2,440,000$ ZZZ & -UPPER, etc. \\
& & & \\ % empty row so that next table section starts on new page

@@

STARDISCMETH\dotfill & String & Method of discovery for the first
planet in the system & \nodata \\

@@

SPECREF\dotfill & & Source of most of the spectroscopic parameters
listed for convenience & SPECURL \\

@@

\tablenotetext{a}{XU, XUPPER, XLOWER, XREF, XURL etc.}
\tablenotetext{b}{Originally as other commonly used name for star in \cite{Wright2011};

@@

\tablenotetext{c}{ZZZ Is this now consistent? ZZZ}

>>>>

% definition of symbols
\def\beq{\begin{equation}}
\def\eeq{\end{equation}}
\def\ergcms{erg~cm$^{-2}$~s$^{-1}$}
\def\ergs{erg~s$^{-1}$}
\def\mps{m~s$^{-1}$}
\def\msun{M_{\odot}}
\def\lsun{L_{\odot}}
\def\etal{~et~al.~}
\def\degree{^{\circ}}
\def\leq{\leqslant}
\def\geq{\geqslant}
\def\micron{$\mu$m}
\def\percm2{{\rm cm^{-2}}}
\def\peryr{yr$^{-1}$}
\def\kepler{\textit{Kepler}}
\def\spitzer{\textit{Spitzer}}
\def\micron{$\mu$m}
\def\mjup{$M_{\rm Jup}$}

@@

%------------------------------------------------------------------------------
Figure: Figure of single planet page, to show updated transit
parameters and RV curves etc.?

%------------------------------------------------------------------------------
\subsection{Revised and Removed Fields}
These include:
OTHERNAME - This is now listed as other name of planet instead of star;
DISCMETH - replaced by planetdiscmeth and stardiscmeth;
S - changed to SHK;
SPSTAR - stellar type of star (unvetted), gone;
NSTEDID - replaced by EANAME (Exoplanet Archive).

@@

%\rotate

@@

  \colhead{Field\tablenotemark{a}} & \colhead{Data Type} & \colhead{Meaning} &
  \colhead{Related Fields\tablenotemark{b}}

@@

OTHERNAME\tablenotemark{c}\dotfill & String & Other commonly used name of planet & \nodata \\

@@

RA\dotfill & Double & J2000 right ascension in decimal hours & \nodata \\
RA\_STRING\dotfill & String & J2000 right ascension in sexagesimal string & \nodata  \\
DEC\dotfill & Double & J2000 declination in decimal degrees & \nodata \\
DEC\_STRING\dotfill & String & J2000 declination in sexagesimal string & \nodata \\

@@

KDE\dotfill & Boolean & If true, planet appears in the \kepler\ archive & \nodata \\
EOD\dotfill & Boolean & If true, planet is included in the EOD & \nodata \\
MICROLENSING\dotfill & Boolean & If true, planet was detected via microlensing & \nodata \\
IMAGING\dotfill & Boolean & If true, planet was detected via imaging & \nodata \\
TIMING\dotfill & Boolean & If true, planet was detected via timing & \nodata \\
ASTROMETRY\dotfill & Boolean & If true, planet was detected via astrometric motion & \nodata \\

@@

DIST\dotfill & & Distance to host star based on parallax in parsecs & -UPPER, etc. \\

@@

T0\dotfill & Double & Epoch of periastron in HJD\tablenotemark{d}$-2,440,000$ & -UPPER, etc. \\

@@

systems only) & -UPPER, etc. \\

@@

function) in \mjup & -UPPER, etc. \\

@@

MASS\dotfill & & Mass of planet in \mjup & -UPPER, etc. \\
SEP\dotfill & & Separation between host star and planet in AU & -UPPER, etc. \\

@@

DEPTH\dotfill & Float & Transit depth, $(R_p/R_*)^2$ & -UPPER, etc. \\

@@

HJD\tablenotemark{d}$-2,440,000$ & -UPPER, etc. \\
R\dotfill & Float & Radius of planet in Jupiter radii & -UPPER, etc. \\
AR\dotfill & & $(a/R_*)$ & -UPPER, etc. \\

@@

GRAVITY\dotfill & Float & $\log{g}$ (surface gravity) of planet in cgs unit &

@@

SE\dotfill & Boolean & If true, at least one secondary eclipse has
been detected & -REF,-URL \\
SEDEPTHJ\dotfill & & Secondary eclipse depth in $J$ band & -UPPER, etc. \\
SEDEPTHH\dotfill & & Secondary eclipse depth in $H$ band & -UPPER, etc. \\
SEDEPTHKS\dotfill & & Secondary eclipse depth in $K_{\rm S}$
band & -UPPER, etc. \\
SEDEPTHKP\dotfill & & Secondary eclipse depth in the
\kepler\ photometry band & -UPPER, etc. \\
SEDEPTH36\dotfill & & Secondary eclipse depth in
\spitzer\ IRAC1 3.6 \micron\ band & -UPPER, etc. \\
SEDEPTH45\dotfill & & Secondary eclipse depth in
\spitzer\ IRAC2 4.5 \micron\ band & -UPPER, etc. \\
SEDEPTH58\dotfill & & Secondary eclipse depth in
\spitzer\ IRAC3 5.8 \micron\ band & -UPPER, etc. \\
SEDEPTH80\dotfill & & Secondary eclipse depth in
\spitzer\ IRAC4 8.0 \micron\ band & -UPPER, etc. \\

@@

HJD\tablenotemark{d}$-2,440,000$ & -UPPER, etc. \\

@@

STARDISCMETH\dotfill & String & Method of discovery of first planet in system & \nodata \\

@@

SPECREF\dotfill & & Source of most of the spectroscopic parameters & SPECURL \\

@@

\tablenotetext{a}{Fields in bold are updates or new additions from
  \cite{Wright2011}. See Section~\ref{sec:update} for more details.}
\tablenotetext{b}{XU, XUPPER, XLOWER, XREF, XURL etc.}
\tablenotetext{c}{Originally as other commonly used name for star in \cite{Wright2011};

@@

\tablenotetext{d}{ZZZ Is this now consistent? ZZZ}
